### 2023-04-27 chapter2/chapter2.tex
Finished last paragraph of introduction

V. Therefore, in this work we apply a series of phylogenetic models to the sequences and molecular features of a set of orthologous IDRs identified in the \textit{Drosophila} genome to dissect the forces driving their evolution. Though the previous approach relied on simulations to generate the null distribution for a hypothesis of no constraint, our analyses of their molecular features instead leverage a fully statistical phylogenetic comparative framework. By comparing models of constrained and unconstrained continuous trait evolution, \textit{i.e.} the Brownian motion and Ornstein-Uhlenbeck models, respectively, we can demonstrate evidence of selective constraint independent of any assumptions about the underlying process of sequence evolution. However, we also explore hybrid approaches that combine simulations with phylogenetic comparative methods to test increasingly refined models of IDR evolution. Our results show IDRs exhibit unique patterns of amino acid substitution where structure-promoting residues are under less constraint in IDRs despite their relative scarcity. Additionally, by treating intrinsic disorder as trait a global analyses of the disorder as trait in some proteins disorder is a dynamically evolving property, with changes in predicted disorder strongly correlated with changes in many distributed features, including hydrophobicity and sequence complexity. Furthermore, we find that while IDRs are unconstrained along several axes of trait evolution, they also reveal conserved patterns of feature constraint which are associated with function, which suggests the previously

>>>>

Therefore, in this work we apply a series of phylogenetic models to a set of orthologous IDRs identified in the \textit{Drosophila} genome to dissect the forces driving their evolution. Our analyses span multiple levels, ranging from the sequences that compose these regions to the distributed features that characterize them as a whole. For the latter, though the previous approach relied on simulations to generate the null distribution for a hypothesis of no constraint, we instead leverage a fully statistical phylogenetic comparative framework. By comparing models of constrained and unconstrained continuous trait evolution, \textit{i.e.} the Brownian motion and Ornstein-Uhlenbeck models, respectively, we can demonstrate evidence of selective constraint on features independent of any assumptions about the underlying process of sequence evolution. However, we also explore hybrid approaches that combine simulations with phylogenetic comparative methods to test increasingly refined models of IDR evolution. We find that IDRs exhibit unique patterns of amino acid substitution and that in some proteins disorder itself is a dynamically evolving property. Furthermore, though IDRs are broadly unconstrained along several axes of feature evolution, we identify specific clusters of IDRs with shared patterns of feature constraint. As in yeast, these clusters are enriched for proteins with specific functional annotations, which suggests the preservation of distributed features and their associated functions is a widespread mechanism of IDR evolution.
